Echoes from the scattering of wavepackets on wormholes

### 2019-01-16 paper.tex
Add files via upload

\begin{equation}
R(\omega)\equiv \frac{||\tilde{\Psi}_{\mathrm{ref}}^{\mathrm{odd}}(\omega)||}{||\tilde{\Psi}_{\mathrm{inc}}^{\mathrm{odd}}(\omega)||}~,~T(\omega)\equiv  \frac{||\tilde{\Psi}_{\mathrm{trans}}^{\mathrm{odd}}(\omega)||}{||\tilde{\Psi}_{\mathrm{inc}}^{\mathrm{odd}}(\omega)||},
\label{eq:odd_ref_and_trans}
\end{equation}
where we compute the one dimensional Fourier transforms of the incident $\tilde{\Psi}_{\mathrm{inc}}^{\mathrm{odd}}(\omega)=\mathcal{F}[\Psi^{\mathrm{odd}}_{\mathrm{bh}}(x,0)]$, reflected $\tilde{\Psi}_{\mathrm{ref}}^{\mathrm{odd}}(\omega)=\mathcal{F}[\Psi^{\mathrm{odd}}_{\mathrm{bh}}(+\infty,t)]$ and transmitted $\tilde{\Psi}_{\mathrm{trans}}^{\mathrm{odd}}(\omega)=\mathcal{F}[\Psi^{\mathrm{odd}}_{\mathrm{bh}}(-\infty,t)]$, where the label (bh) stands for the solutions of the scattering problem of \eqref{eq:wave_tensor_wh} with a single potential barrier. These single barrier solutions are not only necessary for the study of the potential cavity, but also to clean up the low frequency (high $\sigma$) solutions, since in those scenarios it is not simple to determine the amplitude of the echoes. Moreover, All of the aforementioned definitions are also applicable for $\Psi^{\mathrm{even}}$.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=.45\textwidth]{figures/Polarimetry_echo_w_06495.pdf}
\caption{\label{fig:pol} Since phases are random, we compare the Hilbert envelopes of the two clean solutions for echoes. It is possible to see that the outgoing signals have a slight even $(h_+)$ polarization in the intervals shaded in green, and an odd $(h_{\times})$ polarization in the intervals shaded in red. Therefore, the cavity is analog to an optically active medium, changing the polarization of the ingoing Gaussian wavepacket.}
\end{figure}

@@

The small difference in the even and odd potentials is shown in the right panel of Fig.~\ref{fig:evenodd_potentials} has a particular effect in the outgoing waves. In order to illustrate it, we will just work with the even and odd quadrupole signals in the equatorial plane. In the case of a generic spherical mode with equal contributions from $\Psi^{\mathrm{odd}}_{20}$ and $\Psi^{\mathrm{even}}_{20} $, which are the first nontrivial contributions to \eqref{eq:hplus} and \eqref{eq:hx}, we notice that the two polarizations are reduced to

\begin{eqnarray}
h_+(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{even}}_{20}(x,t),\nonumber\\
h_{\times}(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{odd}}_{20}(x,t),\label{eq:pols}
\end{eqnarray}
where $C_{\theta}$ is a constant coming from the normalized spherical harmonics evaluated at $\theta=\pi/2$. Considering $\sigma=0.6495 r_g$, the parameters of the cavity used in sections \ref{sec:scalar} and \ref{sec:tensor} and the same initial Gaussian pulses for $\Psi^{\mathrm{even}}_{20}(x,t)$ and $\Psi^{\mathrm{odd}}_{20}(x,t)$; we show that the existence of echoes generates an outgoing wave with an oscillating net polarization, changing from even $(h_+)$ to odd $(h_{\times})$ polarization throughout the observation time after the transient, as we notice in Fig.~\ref{fig:pol}. It is interesting to notice these effects are present in the echoes solutions for a spherically symmetric system, even when the excess of power is small. Spin-orbit coupling between the spin and the angular momentum in Kerr-like solutions might enhance the polarization effects.

>>>>

\begin{equation}
R(\omega)\equiv \frac{||\tilde{\Psi}_{\mathrm{ref}}^{\mathrm{odd}}(\omega)||}{||\tilde{\Psi}_{\mathrm{inc}}^{\mathrm{odd}}(\omega)||}~,~T(\omega)\equiv  \frac{||\tilde{\Psi}_{\mathrm{trans}}^{\mathrm{odd}}(\omega)||}{||\tilde{\Psi}_{\mathrm{inc}}^{\mathrm{odd}}(\omega)||},
\label{eq:odd_ref_and_trans}
\end{equation}
where we compute the one dimensional Fourier transforms of the incident $\tilde{\Psi}_{\mathrm{inc}}^{\mathrm{odd}}(\omega)=\mathcal{F}[\Psi^{\mathrm{odd}}_{\mathrm{bh}}(x,0)]$, reflected $\tilde{\Psi}_{\mathrm{ref}}^{\mathrm{odd}}(\omega)=\mathcal{F}[\Psi^{\mathrm{odd}}_{\mathrm{bh}}(+\infty,t)]$ and transmitted $\tilde{\Psi}_{\mathrm{trans}}^{\mathrm{odd}}(\omega)=\mathcal{F}[\Psi^{\mathrm{odd}}_{\mathrm{bh}}(-\infty,t)]$, where the label (bh) stands for the solutions of the scattering problem of \eqref{eq:wave_tensor_wh} with a single potential barrier. These single barrier solutions are not only necessary for the study of the potential cavity, but also to clean up the low frequency (high $\sigma$) solutions, since in those scenarios it is not simple to determine the amplitude of the echoes. All of the aforementioned definitions are also applicable for $\Psi^{\mathrm{even}}$.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=.45\textwidth]{figures/Polarimetry_echo_w_06495.pdf}
\caption{\label{fig:pol} Since the phases of the asymptotic solutions are random, we compare the Hilbert envelopes of the two clean solutions for echoes. The outgoing envelopes have a small relative phase shift due to the difference in the potentials, inducing a net even $(h_+)$ polarization in the intervals shaded in green, and an odd $(h_{\times})$ polarization in the intervals shaded in red. Therefore, the cavity is analog to an optically active medium changing the polarization of the ingoing Gaussian wavepacket.}
\end{figure}

@@

The small difference in the Zerilli (even) and Regge-Wheeler (odd) potentials is shown in the right panel of Fig.~\ref{fig:evenodd_potentials} has a particular effect in the outgoing waves. In order to illustrate it, we will just work with the even and odd quadrupole signals in the equatorial plane. In the case of a generic spherical mode with equal contributions from $\Psi^{\mathrm{odd}}_{20}$ and $\Psi^{\mathrm{even}}_{20} $, which are the first nontrivial contributions to \eqref{eq:hplus} and \eqref{eq:hx}, we notice that the two polarizations are reduced to

\begin{eqnarray}
h_+(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{even}}_{20}(x,t),\nonumber\\
h_{\times}(x,t)=\frac{C_{\theta}}{r(|x|)}\Psi^{\mathrm{odd}}_{20}(x,t),\label{eq:pols}
\end{eqnarray}
where $C_{\theta}$ is a constant coming from the normalized spherical harmonics evaluated at $\theta=\pi/2$. Considering $\sigma=0.6495 r_g$, the parameters of the cavity used in sections \ref{sec:scalar} and \ref{sec:tensor} and the same initial Gaussian pulses for $\Psi^{\mathrm{even}}_{20}(x,t)$ and $\Psi^{\mathrm{odd}}_{20}(x,t)$.  As can be noticed in Fig.~\ref{fig:pol}, we show that the difference between the potentials induces a relative phase between the odd and even solutions, generating an outgoing wave with a net polarization oscillating from even $(h_+)$ to odd $(h_{\times})$ and only visible after the transient. It is interesting to notice these effects are present in the echoes solutions for a spherically symmetric system, even when the excess of power is small. Spin-orbit coupling between the spin and the angular momentum in Kerr-like solutions might enhance the polarization effects.
